An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-03 tex/paper.tex
Various additions/edits

To make matters more complicated, often a newly-created strategy is studied in
isolation by opponents chosen by the strategy's creators, and often such
strategies are not sufficiently described to enable realiable recreation
(in the absense of source code), with \cite{slany2007some} being a notable
counter-example. In some cases strategies are revised without updates to their
names or published implementations \cite{li2007design} \cite{li2011engineering}.
As a result, some of the results related to these strategies and tournaments
have not been reliably replicated, and have not met the basic scientific
criterion of falsifiability.

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological tournaments;
    \item Full tournament history.
\end{itemize}

@@

>>>>

To make matters more complicated, often a newly-created strategy is studied in
isolation by opponents chosen by the strategy's creators, and often such
strategies are not sufficiently described to enable reliable recreation
(in the absense of source code), with \cite{slany2007some} being a notable
counter-example. In some cases strategies are revised without updates to their
names or published implementations \cite{li2007design} \cite{li2011engineering}.
As a result, some of the results related to these strategies and tournaments
have not been reliably replicated, and have not met the basic scientific
criterion of falsifiability.

@@

\begin{itemize}
    \item Noisy tournaments
    \item Ecological tournaments
    \item Full tournament history
    \item Creation of plots of distributions of scores and wins
\end{itemize}

@@

S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
hard_majo changes the results). ZD strategies do not fare well in many tournaments.
